title: "Pre-Application Funnel Page Optimization Model"
output: html_notebook
---


The goal of this model is to direct prospects(potential customers) away from pages that will decrease their probability of applying for an account and towards pages that will increase their probability of applying for an account.

The Assumption is that we can takeaway any links from pages restricting the flow of prospects to pages that decrease their probability of applying for an account. Pages that have strong negative impacts will be reviewed with the Product Management team to see if link removal is an option. Pages with strong probability lifts will also be reviewed with Product Management to look for UI opportunities that can maximize customer flow through those node/destination page relationships.


useful:
trace(utils:::unpackPkgZip, edit=TRUE)

Load
```{r}
library(RPostgreSQL)
drv = dbDriver("PostgreSQL")
con = dbConnect(drv,
host = "db.panoply.io",
port = "5439",
user = "rhulsizer@axosbank.com",
password = "XXXX",
dbname = "axosbank_dw")
webdata2 = dbGetQuery(con,"
  SELECT clientid, cifno as CIF, convert(datetime,datehourminute) min, devicecategory, operatingsystem, browser, concat(devicecategory, mobiledeviceinfo) as devicefull, sourcemedium as origin, metro,  pagetitle, pagepath, Right(metro, 2) state
from googleanalytics_cidhitcombined_current
where  hit_type = 'pageview' and convert(datetime,datehourminute) > dateadd(day,-1000,convert(datetime,getdate()))")
```


Clean Data
```{r}
library(dplyr)
library(reconstructr)
library(data.table)
library(dplyr)
library(data.table)
library(purrr)
library(gdata)
library(reshape2)
library(tidyr)
sampledf = webdata2
sampledf = distinct(sampledf)
trim = function (x) gsub("^\\s+|\\s+$", "", x)
sampledf$pagepath = tolower(sampledf$pagepath)
sampledf$pagepath = trim(sampledf$pagepath)
sampledf = sessionise(sampledf, min, clientid, threshold = 1800)
sampledf = sampledf %>% arrange(clientid, session_id, min) 
sampledf$eventid = seq.int(nrow(sampledf))
temp = sampledf
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath1 = dplyr::lag(pagepath, n = 1, default=NA))
sampledf = sampledf %>% filter(!(session.lag.pagepath1 == pagepath) | is.na(session.lag.pagepath1))
temp = temp %>% filter(eventid %in% unique(sampledf$eventid))
sampledf = temp
sampledf$time_delta = NULL
sampledf$session_id = NULL
sampledf = sessionise(sampledf, min, clientid, threshold = 1800)
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath1 = dplyr::lag(pagepath, n = 1, default=NA))
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.eventid = dplyr::lag(eventid, n = 1, default=NA))
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath2 = dplyr::lag(pagepath, n = 2, default=NA))
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath3 = dplyr::lag(pagepath, n = 3, default=NA))
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath4 = dplyr::lag(pagepath, n = 4, default=NA))
sampledf = sampledf %>% group_by(clientid, session_id) %>% mutate(session.lag.pagepath5 = dplyr::lag(pagepath, n = 5, default=NA))
openaccount = subset(sampledf, grepl( 'enrollment', sampledf$pagepath))
notchillpages = subset(sampledf, !grepl( 'axosbanklo', sampledf$pagepath) & !startsWith(sampledf$pagepath, 'apps', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'app', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'axos', trim=T, ignore.case=T)& !startsWith(sampledf$pagepath, 'careers', trim=T, ignore.case=T)& !startsWith(sampledf$pagepath, 'hello', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'homeloans', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'www', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'nationwide.axos', trim=T, ignore.case=T) & !startsWith(sampledf$pagepath, 'web', trim=T, ignore.case=T))
IDs2Remove = as.data.frame(unique(notchillpages$clientid))
colnames(IDs2Remove) = c('clientid')
temp = openaccount %>%
    group_by(clientid) %>%
    arrange(min) %>%
    slice(1L)
IDs2Remove = subset(IDs2Remove, !(clientid %in% unique(factor(temp$clientid))))
sampledf = subset(sampledf, !(sampledf$clientid %in% IDs2Remove$clientid))
temp$applied = 1
temp = temp %>% select(min, applied,  clientid, pagepath) %>% rename(appliedtime = min, enrolledpage =pagepath)
sampledf = left_join(sampledf, temp, by = c("clientid" = "clientid"))
sampledf = subset(sampledf, appliedtime > min | is.na(appliedtime))
sampledf$applied[is.na(sampledf$applied)] = 0
sampledf$state[is.na(sampledf$state)] = 'Unknown'
sampledf$destination = sampledf$pagepath 
sampledf$node = sampledf$session.lag.pagepath1 
sampledf = sampledf %>% unite(link, node, destination)
```


Prepare Data for Modeling/Feature Engineering - Destination Pages
```{r}
nodes = subset(sampledf, !is.na(sampledf$session.lag.eventid)) %>% group_by(session.lag.pagepath1) %>% count() %>% arrange(desc(n))
nodedf = sampledf %>% ungroup() %>% select(applied, pagepath, devicecategory, operatingsystem, browser,  time_delta, session.lag.pagepath1, eventid, state, session.lag.eventid, link, origin, session.lag.pagepath2, session.lag.pagepath3, session.lag.pagepath4, session.lag.pagepath5)
nodedf[] = lapply(nodedf, function(x) if(is.character(x)) factor(x) else x)
destinationdf = subset(nodedf, session.lag.pagepath1=='www.axosbank.com/' | session.lag.pagepath1=='www.axosbank.com/tools/calculators/apy-calculator' |
session.lag.pagepath1=='www.axosbank.com/personal')
pages = destinationdf %>% group_by(session.lag.pagepath1, pagepath) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 5) %>% unite(link,session.lag.pagepath1,pagepath)
destinationdf = subset(destinationdf, (link %in% unique(pages$link)))
nodedf = subset(nodedf, eventid %in% unique(destinationdf$session.lag.eventid))
operatingsystems = destinationdf %>% group_by(session.lag.pagepath1, operatingsystem) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 5) %>% unite(link,session.lag.pagepath1,operatingsystem)
destinationdf$operatingsystem = as.character(destinationdf$operatingsystem)
destinationdf = destinationdf %>% mutate(operatingsystem = replace(operatingsystem, !(paste(session.lag.pagepath1,operatingsystem,sep="_") %in% unique(operatingsystems$link)), "Uncommon"))
destinationdf$operatingsystem = factor(destinationdf$operatingsystem)
browsers = destinationdf %>% group_by(session.lag.pagepath1, browser) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 3) %>% unite(link,session.lag.pagepath1,browser)
destinationdf$browser = as.character(destinationdf$browser)
destinationdf = destinationdf %>% mutate(browser = replace(browser, !(paste(session.lag.pagepath1,browser,sep="_") %in% unique(browsers$link)), "Uncommon"))
destinationdf$browser = factor(destinationdf$browser)
states = destinationdf %>% group_by(session.lag.pagepath1, state) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 9) %>% unite(link,session.lag.pagepath1,state)
destinationdf$state = as.character(destinationdf$state)
destinationdf = destinationdf %>% mutate(state = replace(state, !(paste(session.lag.pagepath1,state,sep="_") %in% unique(states$link)), "Uncommon"))
destinationdf$state = factor(destinationdf$state)
origins = destinationdf %>% group_by(session.lag.pagepath1, origin) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 3) %>% unite(link,session.lag.pagepath1,origin)
destinationdf$origin = as.character(destinationdf$origin)
destinationdf = destinationdf %>% mutate(origin = replace(origin, !(paste(session.lag.pagepath1,origin,sep="_") %in% unique(origins$link)), "Uncommon"))
destinationdf$origin = factor(destinationdf$origin)
temps = destinationdf %>% group_by(session.lag.pagepath1, session.lag.pagepath2) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,session.lag.pagepath1,session.lag.pagepath2)
destinationdf$session.lag.pagepath2 = as.character(destinationdf$session.lag.pagepath2)
destinationdf = destinationdf %>% mutate(session.lag.pagepath2 = replace(session.lag.pagepath2, !(paste(session.lag.pagepath1,session.lag.pagepath2,sep="_") %in% unique(temps$link)), "Uncommon"))
destinationdf$session.lag.pagepath2 = factor(destinationdf$session.lag.pagepath2)
temps = destinationdf %>% group_by(session.lag.pagepath1, session.lag.pagepath3) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,session.lag.pagepath1,session.lag.pagepath3)
destinationdf$session.lag.pagepath3 = as.character(destinationdf$session.lag.pagepath3)
destinationdf = destinationdf %>% mutate(session.lag.pagepath3 = replace(session.lag.pagepath3, !(paste(session.lag.pagepath1,session.lag.pagepath3,sep="_") %in% unique(temps$link)), "Uncommon"))
destinationdf$session.lag.pagepath3 = factor(destinationdf$session.lag.pagepath3)
temps = destinationdf %>% group_by(session.lag.pagepath1, session.lag.pagepath4) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,session.lag.pagepath1,session.lag.pagepath4)
destinationdf$session.lag.pagepath4 = as.character(destinationdf$session.lag.pagepath4)
destinationdf = destinationdf %>% mutate(session.lag.pagepath4 = replace(session.lag.pagepath4, !(paste(session.lag.pagepath1,session.lag.pagepath4,sep="_") %in% unique(temps$link)), "Uncommon"))
destinationdf$session.lag.pagepath4 = factor(destinationdf$session.lag.pagepath4)
temps = destinationdf %>% group_by(session.lag.pagepath1, session.lag.pagepath5) %>% tally() %>% arrange(session.lag.pagepath1 , desc(n)) %>% arrange(session.lag.pagepath1, desc(n)) %>% group_by(session.lag.pagepath1) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,session.lag.pagepath1,session.lag.pagepath5)
destinationdf$session.lag.pagepath5 = as.character(destinationdf$session.lag.pagepath5)
destinationdf = destinationdf %>% mutate(session.lag.pagepath5 = replace(session.lag.pagepath5, !(paste(session.lag.pagepath1,session.lag.pagepath5,sep="_") %in% unique(temps$link)), "Uncommon"))
destinationdf$session.lag.pagepath5 = factor(destinationdf$session.lag.pagepath5)
destinationdf = destinationdf %>% select(session.lag.pagepath1,pagepath,applied, devicecategory, operatingsystem, browser, state, time_delta, origin, session.lag.pagepath2, session.lag.pagepath3, session.lag.pagepath4, session.lag.pagepath5, eventid)
destinationdf[] = lapply(destinationdf, as.character)
destinationdf$session.lag.pagepath2[ is.na(destinationdf$session.lag.pagepath2) ] = "Unknown"
destinationdf$session.lag.pagepath3[ is.na(destinationdf$session.lag.pagepath3) ] = "Unknown"
destinationdf$session.lag.pagepath4[ is.na(destinationdf$session.lag.pagepath4) ] = "Unknown"
destinationdf$session.lag.pagepath5[ is.na(destinationdf$session.lag.pagepath5) ] = "Unknown"
destinationdf$state[ is.na(destinationdf$state) ] = "Unknown"
destinationdf[] = lapply(destinationdf, factor)
destinationdf$time_delta = as.numeric(as.character(destinationdf$time_delta))/60
destinationdf$eventid = as.numeric(as.character(destinationdf$eventid))
```


Partition Destination Page Data
```{r}
samplesize = floor(0.85 * nrow(destinationdf))
set.seed(42)
splitindex = sample(seq_len(nrow(destinationdf)), size = samplesize)
train = destinationdf[splitindex, ]
train = train %>% group_by(session.lag.pagepath1) %>% nest() %>% droplevels()
train = train %>% mutate(data = map(data, ~droplevels(.))) %>% arrange(session.lag.pagepath1)
test = destinationdf[-splitindex, ]
test = test %>% group_by(session.lag.pagepath1) %>% nest() %>% droplevels()
test = test %>% mutate(data = map(data, ~droplevels(.))) %>% arrange(session.lag.pagepath1)
```


Logistic Regression Model for Destination Pages
```{r}
library(broom)
nodemodel = function(df) {
  glm(applied ~ . -	applied - eventid, data = df, family = "binomial", na.action = na.exclude)
}
train = train %>% mutate(mod = map(data, nodemodel))
test$mod = train$mod
train = train %>%
  mutate(prediction = map(mod, predict))
test$mod = train$mod
train = train %>% mutate(
  tidy = map2(.x = mod, .y = data,  .f = ~ tidy(.x, data = .y)),
  glance = map2(.x = mod, .y = data,  .f = ~ glance(.x, data = .y)),
  prediction = map2(.x = mod, .y = data,  .f = ~ predict(.x, type ="response", data = .y, return_df = TRUE))
)
results = test %>% mutate(
  prediction = map2(.x = mod, .y = data,  .f = ~ predict(.x, type ="response", newdata = .y, return_df = TRUE))
)
test = test %>% mutate(
  tidy = map2(.x = mod, .y = data,  .f = ~ tidy(.x, newdata = .y)),
  glance = map2(.x = mod, .y = data,  .f = ~ glance(.x, newdata = .y)),
  augment = map2(.x = mod, .y = data,  .f = ~ augment(.x, newdata = .y))
)
results$mod = NULL
results = unnest(results)
trainresults = train %>% select(data, prediction) %>% unnest() %>% select(eventid, prediction)
destinationresults = union_all(trainresults, results %>% select(eventid, prediction))
results$pred = ifelse(results$prediction > .5,  1, 0)
confusion = table(results$applied,results$pred)
Accuracy = paste('Accuracy is equal to', sum(diag(confusion))/sum(confusion))
Accuracy
confusion
```


Prepare Data for Modeling/Feature Engineering - Node Pages
```{r}
operatingsystems = nodedf %>% group_by(pagepath, operatingsystem) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 5) %>% unite(link,pagepath,operatingsystem)
nodedf$operatingsystem = as.character(nodedf$operatingsystem)
nodedf = nodedf %>% mutate(operatingsystem = replace(operatingsystem, !(paste(pagepath,operatingsystem,sep="_") %in% unique(operatingsystems$link)), "Uncommon"))
nodedf$operatingsystem = factor(nodedf$operatingsystem)
browsers = nodedf %>% group_by(pagepath, browser) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 3) %>% unite(link,pagepath,browser)
nodedf$browser = as.character(nodedf$browser)
nodedf = nodedf %>% mutate(browser = replace(browser, !(paste(pagepath,browser,sep="_") %in% unique(browsers$link)), "Uncommon"))
nodedf$browser = factor(nodedf$browser)
states = nodedf %>% group_by(pagepath, state) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 9) %>% unite(link,pagepath,state)
nodedf$state = as.character(nodedf$state)
nodedf = nodedf %>% mutate(state = replace(state, !(paste(pagepath,state,sep="_") %in% unique(states$link)), "Uncommon"))
nodedf$state = factor(nodedf$state)
origins = nodedf %>% group_by(pagepath, origin) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 3) %>% unite(link,pagepath,origin)
nodedf$origin = as.character(nodedf$origin)
nodedf = nodedf %>% mutate(origin = replace(origin, !(paste(pagepath,origin,sep="_") %in% unique(origins$link)), "Uncommon"))
nodedf$origin = factor(nodedf$origin)
temps = nodedf %>% group_by(pagepath, session.lag.pagepath1) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 5) %>% unite(link,pagepath,session.lag.pagepath1)
nodedf$session.lag.pagepath1 = as.character(nodedf$session.lag.pagepath1)
nodedf = nodedf %>% mutate(session.lag.pagepath1 = replace(session.lag.pagepath1, !(paste(pagepath,session.lag.pagepath1,sep="_") %in% unique(temps$link)), "Uncommon"))
nodedf$session.lag.pagepath1 = factor(nodedf$session.lag.pagepath1)
temps = nodedf %>% group_by(pagepath, session.lag.pagepath2) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,pagepath,session.lag.pagepath2)
nodedf$session.lag.pagepath2 = as.character(nodedf$session.lag.pagepath2)
nodedf = nodedf %>% mutate(session.lag.pagepath2 = replace(session.lag.pagepath2, !(paste(pagepath,session.lag.pagepath2,sep="_") %in% unique(temps$link)), "Uncommon"))
nodedf$session.lag.pagepath2 = factor(nodedf$session.lag.pagepath2)
temps = nodedf %>% group_by(pagepath, session.lag.pagepath3) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,pagepath,session.lag.pagepath3)
nodedf$session.lag.pagepath3 = as.character(nodedf$session.lag.pagepath3)
nodedf = nodedf %>% mutate(session.lag.pagepath3 = replace(session.lag.pagepath3, !(paste(pagepath,session.lag.pagepath3,sep="_") %in% unique(temps$link)), "Uncommon"))
nodedf$session.lag.pagepath3 = factor(nodedf$session.lag.pagepath3)
temps = nodedf %>% group_by(pagepath, session.lag.pagepath4) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,pagepath,session.lag.pagepath4)
nodedf$session.lag.pagepath4 = as.character(nodedf$session.lag.pagepath4)
nodedf = nodedf %>% mutate(session.lag.pagepath4 = replace(session.lag.pagepath4, !(paste(pagepath,session.lag.pagepath4,sep="_") %in% unique(temps$link)), "Uncommon"))
nodedf$session.lag.pagepath4 = factor(nodedf$session.lag.pagepath4)
temps = nodedf %>% group_by(pagepath, session.lag.pagepath5) %>% tally() %>% arrange(pagepath , desc(n)) %>% arrange(pagepath, desc(n)) %>% group_by(pagepath) %>% mutate(rank = row_number()) %>% filter(rank <= 2) %>% unite(link,pagepath,session.lag.pagepath5)
nodedf$session.lag.pagepath5 = as.character(nodedf$session.lag.pagepath5)
nodedf = nodedf %>% mutate(session.lag.pagepath5 = replace(session.lag.pagepath5, !(paste(pagepath,session.lag.pagepath5,sep="_") %in% unique(temps$link)), "Uncommon"))
nodedf$session.lag.pagepath5 = factor(nodedf$session.lag.pagepath5)
nodedf = nodedf %>% select(pagepath, session.lag.pagepath1, applied, devicecategory, operatingsystem, browser, state, time_delta, origin, session.lag.pagepath2, session.lag.pagepath3, session.lag.pagepath4, session.lag.pagepath5, eventid)
nodedf[] = lapply(nodedf, as.character)
nodedf$session.lag.pagepath2[ is.na(nodedf$session.lag.pagepath2) ] = "Unknown"
nodedf$session.lag.pagepath3[ is.na(nodedf$session.lag.pagepath3) ] = "Unknown"
nodedf$session.lag.pagepath4[ is.na(nodedf$session.lag.pagepath4) ] = "Unknown"
nodedf$session.lag.pagepath5[ is.na(nodedf$session.lag.pagepath5) ] = "Unknown"
nodedf$state[ is.na(nodedf$state) ] = "Unknown"
nodedf[] = lapply(nodedf, factor)
nodedf$time_delta = as.numeric(as.character(nodedf$time_delta))/60
nodedf$eventid = as.numeric(as.character(nodedf$eventid))
nodedf$SessionStart = 0
nodedf$SessionStart[ is.na(nodedf$time_delta) ] = 1
nodedf$time_delta[ is.na(nodedf$time_delta) ] = 0
```


Partition Node Page Data
```{r}
samplesize = floor(0.85 * nrow(nodedf))
set.seed(42)
splitindex = sample(seq_len(nrow(nodedf)), size = samplesize)
train = nodedf[splitindex, ]
train = train %>% group_by(pagepath) %>% nest() %>% droplevels()
train = train %>% mutate(data = map(data, ~droplevels(.))) %>% arrange(pagepath)
test = nodedf[-splitindex, ]
test = test %>% group_by(pagepath) %>% nest() %>% droplevels()
test = test %>% mutate(data = map(data, ~droplevels(.))) %>% arrange(pagepath)
```


Logistic Regression Model for Destination Pages
```{r}
library(broom)
nodemodel = function(df) {
  glm(applied ~ . -	applied - eventid, data = df, family = "binomial", na.action = na.exclude)
}
train = train %>% mutate(mod = map(data, nodemodel))
test$mod = train$mod
train = train %>%
  mutate(prediction = map(mod, predict))
test$mod = train$mod
train = train %>% mutate(
  tidy = map2(.x = mod, .y = data,  .f = ~ tidy(.x, data = .y)),
  glance = map2(.x = mod, .y = data,  .f = ~ glance(.x, data = .y)),
  prediction = map2(.x = mod, .y = data,  .f = ~ predict(.x, type ="response", data = .y, return_df = TRUE))
)
results = test %>% mutate(
  prediction = map2(.x = mod, .y = data,  .f = ~ predict(.x, type ="response", newdata = .y, return_df = TRUE))
)
test = test %>% mutate(
  tidy = map2(.x = mod, .y = data,  .f = ~ tidy(.x, newdata = .y)),
  glance = map2(.x = mod, .y = data,  .f = ~ glance(.x, newdata = .y)),
  augment = map2(.x = mod, .y = data,  .f = ~ augment(.x, newdata = .y))
)
results$mod = NULL
results = unnest(results)
trainresults = train %>% select(data, prediction) %>% unnest() %>% select(eventid, prediction)
noderesults = union_all(trainresults, results %>% select(eventid, prediction))
results$pred = ifelse(results$prediction > .5,  1, 0)
confusion = table(results$applied,results$pred)
Accuracy = paste('Accuracy is equal to', sum(diag(confusion))/sum(confusion))
Accuracy
confusion
```






















#####Extra Code

RF Model -- Underperformed vs Logistic Regression
```{r}
nodemodel = function(df) {
  randomForest(factor(applied) ~ ., data = df  ,ntree=20, na.action = na.exclude)
}
train = train %>% mutate(mod = map(data, nodemodel))
train = train %>%
  mutate(prediction = map(mod, predict))
test$mod = train$mod
test$prediction = map2(.x = test$mod, .y = test$data, .f = ~ predict(.x, newdata =.y, return_df = TRUE))
test$mod = NULL
train$mod = NULL
train = unnest(train)
test = unnest(test)
confusion = table(test$applied,test$prediction)
Accuracy = paste('Accuracy is equal to', sum(diag(confusion))/sum(confusion))
Accuracy
confusion
```


Variable Importance
```{r}
library(ggplot2)
importance    = importance(rf_model)
varImportance = data.frame(Variables = row.names(importance), Importance = round(importance[ ,'MeanDecreaseGini'],2))
rankImportance = varImportance %>% mutate(Rank = paste0('#',dense_rank(desc(Importance))))
ggplot(rankImportance, aes(x = reorder(Variables, Importance), y = Importance, fill = Importance)) + geom_bar(stat='identity') + geom_text(aes(x = Variables, y = 0.5, label = Rank), hjust=0, vjust=0.55, size = 4, colour = 'red') + labs(x = 'Variables') + coord_flip() + theme_classic()
```


